On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification

### 2021-03-25 paper/cav_determinisim_main.tex
authors names

\author{Greg Chance, Abanoub Ghobrial, Kevin McAreavey, Severin Lemaignan, Tony Pipe, Kerstin Eder 
\thanks{{\footnotesize
Manuscript  
received ...;
revised ...;  
accepted.... 
Date of publication ...;
date of current version ....

@@

Severin Lemaignan (e-mail: severin.lemaignan@brl.ac.uk)
and
Tony Pipe (e-mail: tony.pipe@brl.ac.uk), 
are with the Bristol Robotics Lab, T Block, University of the West of England,Frenchay, Coldharbour Ln, Bristol, BS34 8QZ, United Kingdom.

>>>>

\author{Greg Chance, Abanoub Ghobrial, Kevin McAreavey, S\'everin Lemaignan, Tony Pipe, Kerstin Eder 
\thanks{{\footnotesize
Manuscript  
received ...;
revised ...;  
accepted.... 
Date of publication ...;
date of current version ....

@@

S\'everin Lemaignan (e-mail: severin.lemaignan@brl.ac.uk)
and
Tony Pipe (e-mail: tony.pipe@brl.ac.uk), 
are with the Bristol Robotics Lab, T Block, University of the West of England,Frenchay, Coldharbour Ln, Bristol, BS34 8QZ, United Kingdom.
